Mechanical loading prediction through accelerometry data during walking and running

### 2022-03-09 manuscript/manuscript.Rmd
Update figures

Afterwards, Bland-Altman plots were built to visualize the agreement between the actual and predicted pGRF and pLR, for both the resultant vector and its vertical component from all accelerometer placements. Bland-Altman plots for the pGRF and pLR resultant vector from hip-worn accelerometers can be seen in Figure 3, and for all accelerometer placements and both resultant and vertical vectors in the Supplemental Figures S3 and S4. Values for all pGRF and pLR prediction equations developed tended to assemble around zero and between the limits of agreement, as shown by the fact that, for all models, at least `r ba_agreement`\% of the data points lie within the limits of agreement. For the pGRF equations, a tendency to higher dispersion can be observed for higher magnitudes, which correspond to the running trials, and especially in values derived from ankle-worn accelerometers (Supplemental Figure S3, Panels A and D). Prediction equations for pLR showed a more accentuated dispersion, and again mainly for higher magnitudes (Supplemental Figure S4). None of the models presented a bias different from zero (*p* > 0.05), demonstrating that they do not consistently over or underestimate the pGRF and pLR values. Although all equations showed a significant proportional bias (*p* < 0.05), the linear regressions presented a low R^2^, with the highest value being `r myround(max(ba_regression_ankle_R2), 2)`.

\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{fig3.png}
		\caption{Bland-Altman plots showing agreement between actual and predicted peak ground reaction force (Panel A) and loading rate (Panel B) for the resultant vector from hip-worn accelerometers. Continuous thick lines show bias (average of the differences between actual and predicted values) while dashed lines show the limits of agreement (bias \pm 1.96 standard deviation). Abbreviations: pGRF, peak ground reaction force; pLR, peak loading rate.}
	\end{measuredfigure}
\end{figure}

>>>>

Afterwards, Bland-Altman plots were built to visualize the agreement between the actual and predicted pGRF and pLR, for both the resultant vector and its vertical component from all accelerometer placements. Bland-Altman plots for the pGRF and pLR resultant vector from hip-worn accelerometers can be seen in Figure 2 (Panels C and D, respectively), and for all accelerometer placements and both resultant and vertical vectors in the Supplemental Figures S3 and S4. Values for all pGRF and pLR prediction equations developed tended to assemble around zero and between the limits of agreement, as shown by the fact that, for all models, at least `r ba_agreement`\% of the data points lie within the limits of agreement. For the pGRF equations, a tendency to higher dispersion can be observed for higher magnitudes, which correspond to the running trials, and especially in values derived from ankle-worn accelerometers (Supplemental Figure S3, Panels A and D). Prediction equations for pLR showed a more accentuated dispersion, and again mainly for higher magnitudes (Supplemental Figure S4). None of the models presented a bias different from zero (*p* > 0.05), demonstrating that they do not consistently over or underestimate the pGRF and pLR values. Although all equations showed a significant proportional bias (*p* < 0.05), the linear regressions presented a low R^2^, with the highest value being `r myround(max(ba_regression_ankle_R2), 2)`.
